\section{Related research}
This section briefly describes related publications. It will later be transformed into a concise narrative for the Background section.

\cite{caliskan2015coding}: authorship identification via ast of decompiled code: metrics?

\cite{moghadam2015autostyle}: style feedback for programming MOOCs. They mention "a range of stylistic mastery" in the abstract.

\cite{choudhury2016scale}: Evaluation of system from \cite{moghadam2015autostyle} in actual course. "students receiving hints via our automated workflow will improve their code quality more in a given period of time".

\cite{fast2014emergent}: Statistical linting and more for Ruby code: extract patterns and idioms, report unusual cases, e.g. of atypical function call co-occurence.

\cite{zhang2014recognizing}: recognize architecture style of buildings (!) from pictures. They extract characteristic "blocklets" and select the most discriminative ones. Interesting as a similar problem in an unrelated domain.

\cite{bumbacher2013student}: extract "coding style" of student programming submissions via a set of features (non-semantic as formatting and semantic as \# of for-loops) and use it to predict help-seeking behavior.

\cite{sung2000memory}: refer to coding style in the context of code generation as "inline/function/...".

% \cite{budiman2019automated}: todo (2019, 0 citations)

% \cite{bonet2018influence}: todo (2018, 0 citations)

\cite{priestley2017ai}: A historical article. They mention the transition of the notion of "style" from a property of programming language to a set of linguistic choices made by a developer in early 1970s.

\cite{karimi2016links}: Refer to the "programming style" as to a broader strategy of programming approach (e.g. breadth-first / depth-first).

\cite{allamanis2014learning}: todo (2014, 149 citations)

\cite{cox2009programming}: todo (2009, 6 citations)

\cite{kondoh2006use}: todo (2006, 3 citations)

\cite{ala2004supporting}: todo (2004, 88 citations)

\cite{ding2004extraction}: todo (2004, 61 citations)

\cite{mohan2004programming}: todo (2004, 17 citations)

\cite{ding2004extraction}: todo ()

\cite{tham2003cilk}: todo (2003, 7 citations)

\cite{krsul1997authorship}: todo (1997, 140 citations)

\cite{oman1990taxonomy, oman1991programming}: todo (1990/91, 80 citations total)

\cite{petre1990languages}: todo (1990, 13 citations)

\cite{oman1989programming}: todo (1989, 47 citations)

\cite{oman1988paradigm}: todo (1988, 33 citations). Maybe group all papers by Oman and Cook? they make for a coherent line of research that somewhat  resembles ours.

\cite{evangelist1984program}: todo (1984, 16 citations)

\cite{kernighan1978elements}: todo (1978, significant book, 763 citations)

\cite{kernighan1974programming}: todo (1974, 50 citations)

















